Transactions Fraud Detection using Machine Learning and Nature Inspired Algorithms

### 2020-05-01 paper/main.tex
Add preprocessing part to paper

% TODO: spomenut preprocessing, co sme robili a co z toho vzislo
% TODO: spomenut transformery, one hot, a filter
% TODO: kolko bol finalny pocet features
% TODO: len kratko spomenut ze preco sme sa rozhodli pouzit aky model - decision tree

>>>>

Before performing experiments, we preprocessed the data. At first, useless columns like id of transaction or those with too many missing values (more than 50\%) are dropped. Our preprocessing pipeline can be devided into two branches - preprocessing of numeric and categorical attributes. In numerical attributes, missing values are filled in with mean value, then all values are normalized (some machine learning algorithms are sensitive to different scales). For categorical attributes, transformation of emails to email domains has been performed, missing values have been filled with most frequent values, small categories (smaller than 5\%) merged into one \textit{other} category and at the end, all features have been one-hot encoded. Also, missing values indicators have been added to both, numerical and categorical attributes.

% TODO: spomenut preprocessing, co sme robili a co z toho vzislo
% TODO: spomenut transformery, one hot, a filter
% TODO: kolko bol finalny pocet features
% TODO: len kratko spomenut ze preco sme sa rozhodli pouzit aky model - decision tree
% TODO: model selection phase
